Output Summary

### 2023-05-02 03-post-process/output-plots.Rmd
Fix small file path bug introduced by recent changes
Very minor: I changed the output file to be called "output_scenario.rds" instead of "output-scenario.rds" in a commit as part of #185
Create new figure settings section in output-plots

# read information from this model
model_info = readRDS(file.path(in_dir, paste0("output-", params$scenario, ".rds")))

@@

>>>>

# read information from this model
model_info = readRDS(file.path(in_dir, paste0("output_", params$scenario, ".rds")))

@@

```{r set-plot-opts}
# select main colors
main_cols = c(
  "model" = "salmon",
  "model2" = "forestgreen",
  "data" = "royalblue"
)

# set the transparent versions based on main color
tran_cols = sapply(main_cols, scales::alpha, alpha = 0.25)

# size of points on figures
pt_cex = 1.4

# figure dimensions: a figure of two panels (inches)
p2_width = 6.5
p2_height = 2.75

# figure dimensions: a figure of three panels (inches)
p3_width = 6.5
p3_height = 2

# figure dimensions: a figure of four panels (inches)
p4_width = 6.5
p4_height = 4.5

# figure dimensions: a figure of 6 panels (inches)
p6_width = 6.5
p6_height = 3.75

# actual ylim to use for [0,1]
# allows showing panel label in upper corner
ylim_01 = c(0, 1.05)
```
